\documentclass[letterpaper]{deedy-resume}  

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------



\namesection{Alexander}{Maru}{ 
\urlstyle{same}\url{http://alexandermaru.com} \\ 
\href{mailto:marua7665@gmail.com}{marua7665@gmail.com} | (226) 220-8798 
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} 

%------------------------------------------------
% Objective
%------------------------------------------------

\section{Objective}
{\bf I am currently seeking an internship\\ for the Winter 2016 term.}\\



%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Undergraduate}

Functional Programming \\
Imperative Programming \\
Modularization \\
Algorithms, Memory and Efficiency \\
Mathematical Proofs \\
Combinatorics \\ 
Probability \\
Calculus I \& II \\
Linear Algebra \\
Logic and Computation \\

%------------------------------------------------

\subsection{High School}

Information and Business \\
Media Arts \\
{\footnotesize \textit{\textbf{(Including Adobe Photoshop \& Illustrator) }}}

\sectionspace 



%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

Github:// \href{https://github.com/assefamaru}{\bf assefamaru} \\
LinkedIn:// \href{https://goo.gl/B7Jwf1}{\bf Alexander Maru} \\
Twitter:// \href{https://twitter.com/assefamaru}{\bf @assefamaru} \\
Quora:// \href{https://www.quora.com/Alexander-Maru}{\bf Alexander-Maru} \\
StackOverflow:// \href{http://stackoverflow.com/users/4739247/alexander?tab=profile}{\bf alexander}

\sectionspace 

\sectionspace 


%------------------------------------------------
% Interests
%------------------------------------------------

\section{Interests}

\subsection{In My Field}

Functional Programming \textbullet{} Cloud \\ Computing \textbullet{} Artificial Intelligence \\ \textbullet{} Machine Learning \textbullet{} Network\\ Security \textbullet{} Applied Mathematics\\ \textbullet{} Combinatorial Analysis \textbullet{} Robotics\\ \textbullet{} Engineering \textbullet{} Mathematical\\ Proofs \textbullet{} Computational Logic\\ \textbullet{} Late Night Coding \textbullet{} Sublime Text \\

\subsection{Other Interests}

Religion \textbullet{} Competitive Chess\\ \textbullet{} Rubike's Cube \textbullet{} Cross-country\\ Running \textbullet{} Travelling \textbullet{} Cultures\\ and Languages \textbullet{} Drawing\\ \textbullet{} Soccer \textbullet{} Philosophy \textbullet{} pi

\sectionspace 

%----------------------------------------------------------------------------------------

\end{minipage}
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} 

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\runsubsection{University of Waterloo}
\descript{| Candidate for Bachelor of Mathematics in Computer Science}

\location{Expected August 2014 - 2019 | Waterloo, Ontario}
\vspace{\topsep} 
\begin{tightitemize}
\item Recipient of President's Scholarship of merit in 2014.
\item Used the UWaterloo API to implement various levels of functional modules using Racket in Designing Functional Programs class in 2014.
\item Compared and analyzed different algorithms for efficiency in Algorithm Design and Data Abstraction course in 2015.
\end{tightitemize}

\sectionspace 

%------------------------------------------------

\runsubsection{Cameron Heights}
\descript{| International Baccalaureate (IB) Program Graduate}

\location{August 2011 - 2014 | Kitchener, Ontario}
\begin{tightitemize}
\item Earned both IB Diploma and Ontario Secondary School Diploma.
\item Received medal for achieving highest score in Business Technology in 2011.
\end{tightitemize}

\sectionspace 

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Ignition}
\descript{| Web Development Coding Camp by Spark Boulder}

\location{February - May 2015 | Boulder, Colorado}
Worked on various front-end and back-end projects to learn the fundamentals of web development. 
Some of the languages and technologies used include HTML5, CSS3, JavaScript, Ruby on Rails, Git, GitHub, Slack and Cloud9.

\sectionspace 

%------------------------------------------------

\runsubsection{YMCA}
\descript{| New Comer Youth Program Volunteer}

\location{August 2011 - 2015 | Kitchener, Ontario}
Lead youth activities and co-ordinated events to engage children between ages 3 - 18, working as a team with other volunteers and staff. Furthermore assisted guest speakers during their presentations by setting up projectors and taking care of any network issues. 

\sectionspace 

% -----------------------------------------------

\runsubsection{Kitchener Youth Action Council (KYAC)}
\descript{| Team Member}

\location{September 2012 - 2014 | Kitchener, Ontario}
Organized the local annual Youth Awards, and collaborated with team members in tackling wide ranging social issues that affected youth in the city, such as homelessness and education.

\sectionspace 



% -----------------------------------------------
% Summary of Qualifications
% -----------------------------------------------

\section{Summary of Skills}
\vspace{\topsep} 
\begin{tightitemize}
\item Proficient in Racket, C, HTML, CSS and Ruby, with some background in JavaScript and PHP.
\item Extensive experience working with frameworks, plugins and technologies such as Ruby on Rails, Bootstrap, JQuery and Cloud9.
\item Familiar with graphics design in Adobe Photoshop, Illustrator and Flash.
\item Fluent in English and Amharic, with some background in Swahili and Spanish.
\item Very committed, and ready to learn and grow in any new environment.
\end{tightitemize}


%------------------------------------------------
% Societies
%------------------------------------------------

\section{Extracurriculars} 
\vspace{\topsep} 
\begin{tightitemize}
\item Was an active member of the following clubs from 2011-2014; Math Club, Chess Club, Multicultural Club, DECA and Spanish Club.
\item Ran with my high school cross-country team for two seasons, qualifying for CWOSSA in the first one.
\end{tightitemize}

\sectionspace 

%----------------------------------------------------------------------------------------

\end{minipage} 

\end{document}